Tuning parameter selection for a penalized estimator of species richness

### 2019-06-14 rre_manuscript/paper.tex

\documentclass[oupdraft]{bio}
% \usepackage[colorlinks=true, urlcolor=citecolor, linkcolor=citecolor, citecolor=citecolor]{hyperref}
\usepackage{url}

% Add history information for the article if required
% \history{Received August 1, 2010;
% revised October 1, 2010;
% accepted for publication November 1, 2010}

\usepackage{amsmath}
\usepackage{xparse}
\usepackage{mathtools}
\usepackage[table]{xcolor}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\ev}[1]{\mathbb{E}\left[#1\right]}
\newcommand{\var}[1]{\text{Var}\left[#1\right]}

% \newcommand{\kmax}{k_{\text{max}}}
% \newcommand{\kmax}[1]{k_{\text{max}(#1)}}
% \newcommand{\kmax}[jj]{k_{\text{max}#1}}

\NewDocumentCommand{\kmax}{o}{%
    {%
        \IfNoValueTF {#1}{
          k_{\text{max}} 
        }{ 
          k_{\text{max}(#1)} 
        }%
    }%
}
\newcommand{\lambdagrid}{\lambda^{\text{grid}}}

@@

% Title of paper
\title{Tuning parameter selection for a penalized maximum likelihood estimator of species richness}

% List of authors, with corresponding author marked by asterisk
\author{ALEX PAYNTER$^\ast$, AMY WILLIS$^\ast$\\[4pt]
% Author addresses
\textit{Department of Biostatistics,
University of Washington,
Health Sciences Building, Box 357232,
1705 NE Pacific St., Seattle, WA 98195}
\\[2pt]
% E-mail address for correspondence
{payntera@uw.edu adwillis@uw.edu}}

% Running headers of paper:
\markboth%
% First field is the short list of authors
{A. Paynter and others}
% Second field is the short title of the paper
{Tuning parameter selection in species richness estimation}

>>>>

\documentclass[oupdraft]{bio}
\usepackage{url}

\usepackage{amsmath}
\usepackage{xparse}
\usepackage{mathtools}
\usepackage[table,dvipsnames]{xcolor}

\usepackage{ifthen}
\usepackage{pstricks}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\kmax}{k_{\text{max}}}
\newcommand{\lambdagrid}{\lambda^{\text{grid}}}

\newboolean{DEBUG}
\setboolean{DEBUG}{true}

\newrgbcolor{amycolor}{.7 .1 .1}
\ifthenelse {\boolean{DEBUG}}
{\newcommand{\amy}[1]{{\bf \amycolor{[\@Amy: #1]}}}}
{\newcommand{\amy}[1]{}}

\newrgbcolor{alexcolor}{.1 .7 .7}
\ifthenelse {\boolean{DEBUG}}
{\newcommand{\alex}[1]{{\bf \alexcolor{[\@alex: #1]}}}}
{\newcommand{\brian}[1]{}}

@@

% Title of paper
\title{Tuning parameter selection for a penalized estimator of species richness}

% List of authors, with corresponding author marked by asterisk
\author{ALEX PAYNTER, AMY D WILLIS$^\ast$\\[4pt]
% Author addresses
\textit{Department of Biostatistics,
University of Washington,
Health Sciences Building, Box 357232,
1705 NE Pacific St., Seattle, WA 98195}
% \\[2pt]
% % E-mail address for correspondence
% {payntera@uw.edu, adwillis@uw.edu}
}

% Running headers of paper:
\markboth%
% First field is the short list of authors
{A. Paynter and A.D. Willis}
% Second field is the short title of the paper
{Tuning parameter selection for species richness}
